A Survey on Ordered Binary Decision Diagrams

### 2015-09-08 paper.tex
Add paragraph to introduction

@@

Nonetheless representing Boolean functions using OBDDs has some drawbacks. Classes
of Boolean functions exist for which the size of the graph grows exponentially,
e.g. integer multiplication~\cite{BRYANT86, BRYANT91, WOELFEL01}.

These limitations of OBDDs motivated researchers to introduce other
representations which e.g. relax the ordering~\cite{BRYANT95} or change the
interpretation of nodes~\cite{BRYANT95}~\cite{ANDERSEN97}. Such representations
may be beneficial for some classes of Boolean functions but mostly suffer from
losing the canonical form and hence the desirable properties OBDDs are famous for.

@@

\section{Citations (temporary)}

\noindent
\par
BRACE90\cite{BRACE90}, BRYANT92\cite{BRYANT92},
\par
RUDELL93\cite{RUDELL93}, BOLLIG96\cite{BOLLIG96}

>>>>

Bryant also introduced and experimentally evaluated efficient implementation
techniques for OBDDs in collaboration with Brace and
Rudell~\cite{BRACE90, BRYANT92}.

@@

Nonetheless representing Boolean functions using OBDDs has some drawbacks. Classes
of Boolean functions exist for which the size of the graph grows exponentially
independent of the variable ordering, e.g. integer
multiplication~\cite{BRYANT86, BRYANT91, WOELFEL01}.

These limitations of OBDDs motivated researchers to introduce heuristics and
other techniques like \textit{dynamic variable ordering}~\cite{RUDELL93} to solve
the problem of variable ordering~\cite{BOLLIG96}. Furthermore, alternative
representations which e.g. relax the ordering~\cite{BRYANT95} or change the
interpretation of nodes~\cite{BRYANT95, ANDERSEN97} were developed. Such
representations may be beneficial for some classes of Boolean functions but mostly
suffer from losing the canonical form and hence the desirable properties OBDDs
are famous for.

@@
